---
title: "Week_1 R for Reproducible Scientific Analysis"
author: "James Johnson"
date: "June 20, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Welcome!

- If you haven't already - please sign up for Rstudio cloud!
- This is my first time running so it will not be without hiccups.
- [This article summarizes the learning philosophy we'll be using](https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1006023)

## What are we here to do?

- We will be learning a workflow in R
- this will include learning about the R language, using R to explore and visualize a dataset and getting acquainted with R's modern workflow

## What won't we cover?

- This will *NOT* be an extensive treatment of statistics

## What should you be doing?

- Try to establish your own learning goals:
    - I would suggest trying to identify something you already do in excel or SAS, and trying to do the same thing in R
    - Expect this be to slower than your normal workflow at first! You are learning a language.

##
## Slide with Plot

```{r pressure}
plot(pressure)
```

